\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}
\name{Hakan ``John" Can  Gunerli}
\program{Computer Science Major}
\contact{Personal Email: hakancangunerli@gmail.com \hspace{2cm} 415-323-6804 \hspace{2cm}Student Email: hgunerli1@student.gsu.edu}
\contact{GitHub: hakancangunerli  \hspace{2cm} LinkedIn: hakancangunerli}
\contact{BitBucket : hakancangunerli}
\end{resume_header}

\begin{resume_section}{About Me}
  \begin{nospacetabbing}
  \textbf{Programming}  \=Proficient in: Python 3, , Java Familiar with: JavaScript, C\#, \LaTeX\\
  \textbf{Interests} \>Etymology, History, Digital Hoarding, Scientific Research, Storm Chasing, UX Design\\* 
  \end{nospacetabbing}
\end{resume_section}
\begin{resume_section}{Work Experience}

\begin{resume_employer}{Software Engineering Intern}{Türkiye İş Bankası A.Ş.
}{Istanbul, Turkey}{September 2020-Present}
 \item Interned at payment processing, one of the backbones of the company's profit areas. 
 \item Worked with a team of 5 engineers on POS orchestration software.
 \item Used C# in the backend and Angular in the frontend to create a visual JSON connection program.
\item Languages used: Angular, C\#
\item Systems used: MongoDB, .NET
    \end{resume_employer}
      \begin{resume_employer}{Co-Founder, CEO}{tal-labs}{Atlanta, GA }{May 2019 -Currently}
    
    \item tal-labs was formulated to create products and services for the productivity sector.
\item Currently a team of 6 Software Engineers, tal-labs aims to provide services for people who just need more management and order in their lives.

  \end{resume_employer}
    
 \begin{resume_employer}{Course Instructor}{theCoderSchool}{Johns Creek, GA}{August 2019-Present}
  \item  -Assess and look after 50+ students' progress throughout the year and design projects with other staff to create an immersive teaching experience.

  \item Plan the content to be covered in the class according to the curriculum, the number of weeks available and the date of project deadlines.
  \item Taught web development, web design, mobile development, graphical user interface design and web application design

  \item Frameworks taught: React, Bootstrap, Django, Flask,
  \item Languages taught: Scratch, Snap!, Python, JavaScript, C#
    \end{resume_employer}
    
 
    
    
  \begin{resume_employer}{Cloud DevOps Engineer}{uVox Inc.}{Alpharetta, GA}{May 2019-Present}
\item Work with a team of 5 engineers in development and migration to the cloud.
\item Implemented tools in GCP and in Docker containers.
\item Created reports and reported to the CEO directly about possible technologies to be implemented.

\item Tech used: GCP, AWS, Python3, Linux
    \end{resume_employer}
   
  


 


  
\end{resume_section}
\begin{resume_section}{Community Involvements}
 \begin{resume_employer}   {Front-end Developer}{American Red Cross}{Washington D.C.}{May 2019-Present}
    \item Help the programming team maintain the design and structure of the website.
    \item Use Adobe Experience Cloud for content and audience management.
  \end{resume_employer}



\end{resume_section}


\begin{resume_section}{Education}
  \begin{resume_subsection}[Atlanta, GA (2019--Present)]{Georgia State University: Honors College }
    \begin{subitems}
       \item Computer Science \textit{Bachelor of Science, 3.9/4.30 GPA }  Expected December 2023
       \item Computer Science Club President, PantherHackers Member
    \end{subitems}
  \end{resume_subsection}

\end{resume_section}

\begin{resume_section}{Certifications}
  \begin{nospacetabbing}

  \textbf{Programming Certifications}  \= University of Michigan: Python Data Structures, deeplearning.io: Artificial Intelligence
  \end{nospacetabbing}
\end{resume_section}
\end{document}
